An institutional approach to attention allocation and venture resource mobilization and acquisition

### 2021-03-15 Manuscript.Rmd
Finalizing manuscript

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

@@

## Measures

@@

@@

@@

@@

## Data
The dataset from the Global Accelerator Learning Initiative (GALI) covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020. Our data include information – collected during program applications – about ventures, founding teams, and pre-program performance. They also identify which applicants went on to participate in each program. Finally, these data include follow-up information collected from selected and rejected applicants in the years following each application window. The anonymized dataset containing both application and follow-up data can be accessed at [GALI Data](www.galidata.org/data-request). This is multi-country dataset. It typically contains hundreds of ventures per country.

I set aside XXX nonprofit organizations and XXX observations that are missing relevant venture information or preference ranking, resulting in xxx observations in the final sample. All financial statistics are in United States Dollars (USD). ********

## Methods
The ventures in our sample are nested within countries. To account for such nested (or hierarchical) structure of the data, I opt for a linear mixed effects model to estimate the effects of each resource alone and when it interacts with institutional level of the resource.  This helps us account for fixed effects and random effects associated with non-nested grouping factors. Namely, it allows us to take into account the institutional (i.e. country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.

The following equation (formulas) show all the models by outcome category. Of note, I run all the following models with conrols and without controls as robustness check. Control vriables are HCI refering to Human Capital Index and GC refering to Gender composition (i.e. female percentage in a team).

@@

(1)	*Participated ~  AHC + (AHC | Country)    ; AHC = Attention to Human Capital* 
(2)	*Participated ~  AHC + (AHC x Ease of finding skilled employees | Country)*
(3)	*Participated ~  AFC + (AFC | Country)   ; AHC = Attention to Financial Capital*
(4)	*Participated ~  AFC + (AFC x Financing of SMEs| Country)*   
(5)	*Participated ~  AFC + (AFC x VC availability | Country)*   
(6)	*Participated ~  AFC + (AFC x Domestic Credit Gaps | Country)*   
(7)	*Participated ~  ASC + (ASC | Country) ; ASC = Attention to Social Capital*   
(8)	*Participated ~  ASC + (ASC x State of cluster development | Country)*

@@

(9) *Total employees ~ AHC + (AHC | Country)*
(10) *Total employees ~ AHC + (AHC x Ease of finding skilled employees | Country)*
(11) *Capital Raised ~ AFC + (AFC | Country)* 
(12) *Capital Raised ~ AFC + (AFC x Financing of SMEs| Country)*
(13) *Capital Raised ~ AFC + (AFC x VC availability | Country)*
(14) *Capital Raised ~ AFC + (AFC x VC availability | Country)*
(15) *Capital sources ~ ASC + (ASC | Country)*   
(16) *Capital sources ~  ASC + (ASC x State of cluster development | Country)*

@@

(17)	*Revenue ~  AHC + (AHC | Country)* 
(18)	*Revenue ~  AHC + (AHC x Ease of finding skilled employees | Country)*
(19)	*Revenue ~  AFC + (AFC | Country)*
(20)	*Revenue ~  AFC + (AFC x Financing of SMEs| Country) + (AFC x VC availability | Country) + (AFC x Domestic Credit Gaps | Country)*   
(23)	*Revenue ~  ASC + (ASC | Country)*   
(24)	*Revenue ~  ASC + (ASC x State of cluster development | Country)*

@@

a  %>%
  ggplot(aes(Score)) +
  geom_bar() +
  facet_grid(~Attention) +
  theme_bw()

@@

a  %>%
  ggplot(aes(Score)) +
  geom_bar() +
  facet_grid(vars(`Income group`), vars(Attention)) +
  theme_bw()

@@

filter(b, Attention == "Network")  %>%
  ggplot(aes(Score, `Total Equity Sources`)) +
  geom_point()  +
  facet_grid(~`Income group`)+
  theme_bw()

filter(b, Attention == "Direct Funding")  %>%
  ggplot(aes(Score, `Capital Raised`)) +
  geom_point()  +
  facet_grid(~`Income group`)+
  theme_bw()

@@

kable(hc_zero, escape = F, caption = "Effect of attention to human capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kable(hc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of human capital", format = "latex") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(fc_zero, escape = F, caption = "Effect of attention to financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level (SME financing) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(fc_two, escape = F, caption = "Effect of congruency of venture attention and institutional level (VC) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(fc_three, escape = F, caption = "Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(sc_zero, escape = F, caption = "Effect of attention to social capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(sc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of social capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

@@

# Discussion

>>>>

abstract: |
  Early stage entrepreneurs have access to limited resources and must decide what should garner their attention. The literatures on entrepreneurial resources and entrepreneurial attention show mixed results and often do not take into account the institutional context of the venture. I approach the question of entrepreneurial attention from an institutional perspective using the Global Accelerator Learning Initiative Data. In contrast to expectation based on the literature, I find that entrepreneurs do not have to align their attention to resources with the availability of resources in their institutional environment. However, their attention to internal human capital (i.e. building their own business skills) becomes important if we consider the outcome as being selection to an incubation program to mobilize resources and prepare for long-term resource acquisition. Resource acquisition is a long-term goal and that is why I do not see any effects in the short term. In contrast, selection to an incubation program is a short-term goal that opens the door for the long-term effects and that is how  early stage ventures should approach their resource base strategy. Mobilization comes first and acquisition would follow. Thus, the question is not what resources to seek, but when to seek mobilization and when to engage in acquisition of a resource.

@@

## Data and Measures
The dataset from the Global Accelerator Learning Initiative (GALI) covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020. Our data include information – collected during program applications – about ventures, founding teams, and pre-program performance. They also identify which applicants went on to participate in each program. Finally, these data include follow-up information collected from selected and rejected applicants in the years following each application window. The anonymized dataset containing both application and follow-up data can be accessed at [GALI Data](www.galidata.org/data-request). This is multi-country dataset. It typically contains hundreds of ventures per country.

The initial sample consists of 22,928 venture from 73 countries. I set aside nonprofit organizations and  observations that are missing relevant venture information or preference ranking, resulting in 15981 observations in the final sample. All financial statistics are in United States Dollars (USD).

@@

Figure 3 shows us the distribution of venture attention to resources by type of resource. We observe that the majority of entrepreneurs focus their attention on direct finding, access to investors and general networking. Business training comes second in the entreprenerus radar. Credibility and access to peers are the two resources that entrepreneurs rank the lowest in their preference and thus they do not pay attention to acquiring these resources. Figure 4 helps us dive in into this distribution by classification of country in terms of income (High income, upper middle income, lower middle income, and low income). We see that the distribution is very similar regardless of the country classification.

@@

Figure 1 displays all countries in the sample with their positioning along the three dimensions of institutional capital. We see that the United States has the highest scores along all three dimensions, meaning that it has a strong infrastructure in terms of all three of forms of capital. This explains the mixed results of the research on attention capital given that the majority of this literature is based in the US context. Namely, entrepreneurs in the US operate within a rich resource environment and attention to resources depends more in their own strategy and initial resource capital rather than their institutional level captial. On the other side of the figure we find Angola as the country with lowest scores along all the dimension of institutional level capital. Figure 2 zooms in to get a closer look at the group of countries positioned in the middle at the center of figure 1.

@@

Figure 5 shows us the correlation between the venture network (i.e. total equity sources) and the venture attention level to network by country classification. Similarly, Figure 6 shows us the correlation between the venture's total capital raised and the its attention level to direct funding by country classification.

@@

## Methods
The ventures in the sample are nested within countries. To account for such nested (or hierarchical) structure of the data, I opt for a linear mixed effects model to estimate the effects of each resource alone and when it interacts with institutional level of the resource.  This helps us account for fixed effects and random effects associated with non-nested grouping factors. Namely, it allows us to take into account the institutional (i.e. country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.

The following equations show all the models by outcome category. Of note, I run all the initial models (i.e. resource mobilization models) with conrols and without controls as robustness check. Control vriables are the Human Capital Index and Gender composition (i.e. female percentage in a team) that were highlight in the previous section about measures. AHC, AFC, and ASC refer to our key predictors; Attention to Human Capital, Attention to Financial Capital, and Attention to Social Capital respectively.

@@

$${Participated_i} =  \beta_0 + b AHC_i + Controls_i + \epsilon_i $$

$${Participated_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ Controls_i + \epsilon_i $$
$${Participated_i} =  \beta_0 + b AFC_i +Controls_i + \epsilon_i $$   
$${Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c+ Controls_i + \epsilon_i $$
$${Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * VC availability_c+ Controls_i + \epsilon_i $$
$${Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Domestic Credit Gaps_c+ Controls_i + \epsilon_i $$
$${Participated_i} =  \beta_0 + b ASC_i + Controls_i + \epsilon_i $$
$${Participated_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ Controls_i + \epsilon_i $$

@@

$${Total Employees_i} =  \beta_0 + b AHC_i + \epsilon_i $$
$${Total Employees_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ \epsilon_i $$
$${CapitalRaised_i} =  \beta_0 + b AFC_i + \epsilon_i $$ 
$${CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c + \epsilon_i $$
$${CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * VC availability_c + \epsilon_i $$
$${CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Domestic Credit Gaps_c + \epsilon_i $$
$${CapitalSources_i} =  \beta_0 + b ASC_i + \epsilon_i $$ 
$${CapitalSources_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ \epsilon_i $$

@@

$${Revenue_i} =  \beta_0 + b AHC_i + \epsilon_i $$ 
$${Revenue_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ \epsilon_i $$
$${Revenue_i} =  \beta_0 + b AFC_i + \epsilon_i $$ 
$${Revenue_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c + b_3 AFC_i * VC availability_c + b_4 AFC_i * Domestic Credit Gaps_c + \epsilon_i $$
$${Revenue_i} =  \beta_0 + b ASC_i + \epsilon_i $$
$${Revenue_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ \epsilon_i $$

@@

a  %>%
  ggplot(aes(Score)) +
  geom_bar() +
  facet_grid(~Attention) +
  theme_bw()+
  ylab("")+
  xlab("Attention score")

@@

a  %>%
  ggplot(aes(Score)) +
  geom_bar() +
  facet_grid(vars(`Income group`), vars(Attention)) +
  theme_bw() +
  ylab("")+
  xlab("Attention score")

@@

filter(b, Attention == "Network")  %>%
  ggplot(aes(Score, `Total Equity Sources`)) +
  geom_point()  +
  facet_grid(~`Income group`)+
  xlab("Attention to Network")+
  theme_bw()

filter(b, Attention == "Direct Funding")  %>%
  ggplot(aes(Score, `Capital Raised`)) +
  geom_point()  +
  facet_grid(~`Income group`)+
  xlab("Attention to Direct Funding")+
  theme_bw()

@@

kable(hc_zero, escape = F, caption = "Effect of attention to human capital on likelihood of participation") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kable(hc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of human capital on likelihood of participation", format = "latex") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(fc_zero, escape = F, caption = "Effect of attention to financial capital on likelihood of participation") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level (SME financing) of financial capital on likelihood of participation") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(fc_two, escape = F, caption = "Effect of congruency of venture attention and institutional level (VC) of financial capital on likelihood of participation") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(fc_three, escape = F, caption = "Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital on likelihood of participation") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(sc_zero, escape = F, caption = "Effect of attention to social capital on likelihood of participation") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(sc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of social capital on likelihood of participation") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

@@

# Results and Discussion
**Resource mobilization**

I find no support for hypothesis 1, with exception for certain resources. Specifically, Table 1 shows that an increase in venture attention to human capital causes an increase in the venture's likelihood to participate to the acceleration program and mobilize resources. However, this effect is not statistically significant. The model is robust to the addition of control variables. Similarly, table 7 show that an increase in venture to attention social capital causes an increase in the venture's likelihood to mobilize resources within the acceleration program. These effects are not statistically signification. Table 3 on the other hand, show that an increase in venture attention to social capital results in a significant decrease in the venture's likelihood to mobilize resources. This shows that early stage ventures applying to accelerator programs benefit the most if they first focus on mobilizing human and social capital resources before turning attention to financial capital. To examine our hypotheses exploring these same relationships within the institutional context of the venture, we turn to tables 2, 4, 5, 6, and 8. When I interact the venture level attention to human capital with the institutional level human capital (Table 2), I find that attention to this resource results in a significant increase in the likelihood to mobilize resources within the accelerator program ($b = 0.9$), and the model is robust to control variables. In contrast, tables 3 to 5 show that attention to financial capital has a non-significant effect on the venture's likelihood to mobilize resources regardless of the institutional context. We find the same results whether we consider institutional level capital for SMEs, VC oriented ventures, or ventures seeking loans and other forms of financing from financial establishments. This is in line with our initial finding that human and social capital should garner the attention of ventures seeking resources in their early stage from incubators and accelerators. Finally, table 8 shows us that the congruency of venture attention and the institutional level of social capital does not have any significant effect on the venture's likelihood to mobilize resources.

This first part of the analysis focuses on resource mobilization within accelerator programs and explores the relationship between venture attention to a certain type of resources and its influence on the venture's likelihood to participate to the program. I find that social and human capital are the key resources that should be on the venture's radar in their early stage of strategy formation. I then investigate the impact of the congruency between the venture attention and the institutional level capital to better understand these relationships within their institutional context. I find that human capital is not only one of the key resources to focus on but it becomes even more important if it aligns with the venture's country to provide skillful human resources.

Similar to hypothesis 1, I find no support for the second hypothesis. Table 9 shows the impact of venture attention to human capital and its congruency level with the institutional capital on the acquisition of human capital (total number of employees) post-acceleration program. I find no significant effect in the two models. Tables 10 to 12 show the impact of venture attention to financial capital and its congruency level with the institutional capital on the acquisition of financial capital (capital raised in USD) post-acceleration program. I find no significant effect in the two models. Finally, table 13 shows the the impact of venture attention to social capital and its congruency level with the institutional capital on the acquisition of social capital (sources of capital) post-acceleration program. I find no significant effect in the two models.

It is important to highlight here, that not only I find no significant effect but also all the coefficients are negative. This negative effect on resource acquisition post-acceleration program can be interpreted economically, as an opportunity cost. Ventures that succeed in mobilizing resources put their time and efforts into acquiring business skills, developing their network, and seeking funding resources. While these efforts might result in resource acquisition, over the long-term, we would not be able to observe this within a year or two post resource mobilization. This is a key limitation of our data and analysis.

Based on the results of resource acquisition we would expect similar results for venture performance (hypothesis 3) since revenues are often accumulated post resource acquisition. We can consider this part of the analysis as a robustness check for the previous analysis on resource acquisition. Tables 14 to 16 confirm these expectations. I find only null effects of the impact of venture attention to a resource and its congruency level with the institutional level of the resource on performance (measured based on firm revenues) post acceleration program.

There are several channels to interpret the results of all three outcomes. The most plausible explanation is that at their early stages of venturing, entrepreneurs do not have to align their attention to resources with the availability of resources in their institutional environment. However, their attention to internal human capital (i.e. building their own business skills) becomes important if we consider the outcome as being selection to an incubation program instead to mobilize resources and prepare for long-term resource acquisition. Resource acquisition is a long-term goal and that is why I do not see any effects in the short term (2 years post acceleration). In contrast, selection to an incubation program is a short-term goal that opens the door for the long-term effects and that is how ventures in our sample should approach their resource base strategy (i.e. mobilization first and acquisition would follow).
